---
title: "ICY0006 Probability And Statistics - Exercise 1"
output:
  html_document:
    df_print: paged
---

This is Exercise 1 from ICY0006 course - Probability And Statistics

Exercise is as follows:\
You have randomized 2 groups of patients, A and B, who take two drugs (A\
and B, respectively). From each patient you measure blood sugar (smaller\
values are better). Please analyse these data and plot the results. Explain\
your analytic choices. What do you conclude from you analysis?\
A) Is drug A reliably different from drug B? explain you answer.\
B) In the absence of other evidence, (i) is it more likely that A is better\
than B, or (ii) is it more likely that B is better, or (iii) does evidence point\
to A and B being equal, or (iv) is it true that we cannot say either way,\
based on available evidence.\
C) If you needed to take either drug A or B, which one would you choose\
(or would you just toss a coin to make the choice).\
D) Suppose that your sample size would have been 50, instead of 5. Would\
you have plotted the data differently? if yes, how? Would you have analysed\
the data differently in any way? if yes, explain how and why.\
E) Suppose that your sample size would have been 500, instead of 5. Would\
you have plotted the data differently? if yes, how? Would you have analysed\
the data differently in any way? if yes, explain how and why.


| Group | Value |
|:---:|:---:|
|A | 0.2273642|
|A | 0.1700281|
|A | 0.3781713|
|A | 0.6344903|
|A | 0.9484044|
|B | 1.7099361|
|B | 5.7520838|
|B | 0.3314107|
|B | 0.9291784|
|B | 2.8027043|

And we initialize the values for further use:

```{r}
A <- c(0.2273642,0.1700281,0.3781713,0.6344903,0.9484044)
B <- c(1.7099361, 5.7520838, 0.3314107, 0.9291784, 2.8027043)
```


# A) Is drug A reliably different from drug B? explain you answer.


```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
